Quality measure notes

### 2021-09-21 StateOfPractice/Ao-Report/02ack.tex
MI report - updated acknowledgements

acknowledgements here

>>>>

I would like to express my appreciation to my instructors, Dr. Spencer Smith and Dr. Jacques Carette, for guiding me through the research and report writing. I also would like to thank other members of our team, Peter Michalski, Oluwaseun Owojaiye, and Dr. Michael Noseworthy.

I have my special thanks to my wife, who has always been considerate and supportive during the whole of my graduate study.
